Policy Costs \\ \pa{ Target Journals: Ecological Applications, Journal of Applied Ecology, some discussion of whether scope for PNAS}

### 2013-05-13 inst/doc/policycosts/policycosts_PRA.tex
Tex version with comments from Paul

\documentclass[authoryear, review, 12pt]{elsarticle}
\usepackage{amssymb,amsmath,amsfonts,graphicx}
\bibliographystyle{elsarticle-harv}
%\usepackage{natbib} % already loaded by elsarticle
%\biboptions{sort&compress} % For natbib
%\usepackage{hyperref} % already loaded by elsarticle
%\hypersetup{breaklinks=true, pdfborder={0 0 0}}

\usepackage[hyphens]{url}

@@

\usepackage[pdftex, usenames]{color}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\cdb}[1]{{\it \color{darkgreen} #1}}
\newcommand{\pa}[1]{{\it \color{darkblue} #1}}

\begin{document}
\begin{frontmatter}
\title{Policy Costs}
\author[cpb]{C. Boettiger\corref{cor1}}
\ead{cboettig@ucdavis.edu}
\author[melbourne]{M. Bode}
\author[esp]{J. Sanchirico}
\author[utk-econ]{J. LaRiviera}
\author[cpb,esp]{A. Hastings}
\author[utk-eeb]{P. Armsworth}
\cortext[cor1]{Corresponding author}
\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}
\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
Parkville, Melbourne, VIC 3010, Australia}

\begin{abstract}
\cdb{Carl's comments \& questions added in green}
\end{abstract}
\begin{keyword}
  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
\end{keyword}

@@

(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time).

@@

@@

\begin{itemize}
  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
    \begin{equation} 
      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t}, 
    \end{equation}
where $Z_t$ gives the stochastic shocks.  $Z_t$ may be distributed log-normally \footnote{though this violates the self-sustaining property of~\citet{Reed1979}, such that the optimal constant-escapement level $S$ in the stochastic model is greater than the optimal escapement in the deterministic scenario.}

\item   Fishing profit function 
  \begin{equation} 
    \Pi_0(x,h) = p h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \label{profit}
  \end{equation}
  where $h$ is the harvest level, $x$ the stock size, $h/x$ represents
  fishing effort, $p$ the price per unit harvest.  The coefficient $c_1$
  introduces a quadratic cost to effort, a typical way to introduce
  smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 =
  c_1 = 0$.

\item
Policy cost function: L1, L2, fixed fee, asymmetric, are introduced
as modifications to the cost function that depend on the action
taken in the previous time-step.  (This makes the previous action part
of the state space).   All cost functions are characterized in terms
of the coupling coefficient $c_2$.  (Because $c_2$ takes different units
and strength of interaction under the different functional forms, it is
necessary to calibrate the choice of this coefficient such that these
penalties can be compared directly, as described in the next section.)

@@

\item   Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.  
\item   Choice of model parameters 
\end{itemize}

@@

% From Jake:

The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.  Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.  
To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).  By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.  For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.  As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.  Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.  One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.

@@

%% end-Jake

@@

@@

@@

\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
%Must be nonlinear somewhere when adjustment costs exceed profits?

@@

\pa{
   
  \textbf{Option 1.}

@@

  We include a version of the results Carl currently shows in his Fig 5 and 6 for the L1 penalty, but we include it also for the other penalty function forms – e.g. using Carl’s suggestion of a box-whisker plot.
   
  Reminder - The two figures compare the performance of the optimal policy when accounting for the policy adjustment costs (maximizing $\Pi_{L_1}$) with what the optimal policy recommendation one would arrive if ignoring these costs (maximizing $\Pi_0$) WHEN scoring the performance of the two control recommendations against $\Pi_{L_1}$.
   
  Fig. 5 shows the breakdown into how the gross yield (ph) and adjustment cost ($c_2 abs(h_t-h_{t-1})$) separately. The policy ignoring costs of policy adjustment gets higher gross yields by tracking the variations more closely but also incurs (even) higher policy adjustment costs. Fig 6 combines the two bits to show the effect on net present value.
   
  This option would let one answer:

@@

  We populate a table that organizes columns by the ``Actual functional form of adjustment costs'' and the rows into ``Assumed functional form of adjustment costs.'' The types of functional form in both columns and rows would then run ``None, $L_1$, $L_2$ etc.''
   
  IF we denote the optimal control for objective function $NPV_i$ as being $h^*_i$, then I would populate the Table with the proportions
  $NPV_i(h^*_j) / NPV_i(h^*_i)$
  (i.e. what proportion of the available NPV you still get if assuming the wrong functional form for the adjustment costs).
   
  The inclusion of the comparison against None means that all of what was being talked about for Option 2 would be captured. In addition it would provide a robustness check on a policy recommendation if uncertain of either the presence of policy adjustment costs or functional form that they should adopt. Specifically, by comparing across rows one could ascertain whether assuming one choice of functional form was likely to lead to large efficiency costs should other assumptions about adjustment costs prove correct. Similarly one could compare across columns to see if one form were particularly problematic in reality.
   
  I don’t know if those are clear – you need to get mired into the document once again a bit to parse it out. I’ll happily discuss with anyone in a bid to shed more light.
   
  Discussion of these options and alternative suggestions invited.
}

@@

\section{Discussion}
\cdb{Some possible things to discuss: could add others, could remove some.}
\begin{itemize}
\item   Comparison of the optimal policy solution to the Reed model
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and de-stablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
\item   Impact of symmetric vs asymmetric costs
\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
\end{itemize}

>>>>

\documentclass[authoryear, review, 12pt]{elsarticle}
\usepackage{amssymb,amsmath,amsfonts,graphicx}
\bibliographystyle{elsarticle-harv}
\usepackage{natbib} % already loaded by elsarticle
\biboptions{sort&compress} % For natbib
\usepackage{hyperref} % already loaded by elsarticle
\hypersetup{breaklinks=true, pdfborder={0 0 0}}

%\usepackage[hyphens]{url}

@@

\usepackage[pdftex, usenames]{color}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\cdb}[1]{{\it \color{darkgreen} #1}}
\newcommand{\pa}[1]{{\it \color{darkblue} #1}}
\newcommand{\jr}[1]{{\it \color{darkred} #1}}

\begin{document}
\begin{frontmatter}
\title{Policy Costs \\ \pa{
Target Journals: Ecological Applications, Journal of Applied Ecology, some discussion of whether scope for PNAS}}
\author[cpb]{C. Boettiger\corref{cor1}}
\ead{cboettig@ucdavis.edu}
\author[melbourne]{M. Bode}
\author[esp]{J. N. Sanchirico}
\author[utk-econ]{J. LaRiviere}
\author[cpb,esp]{A.M. Hastings}
\author[utk-eeb]{P. R Armsworth}
\cortext[cor1]{Corresponding author, present address: XXX}
\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
Parkville, Melbourne, VIC 3010, Australia}
\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}

\begin{abstract}
\cdb{Carl's comments \& questions added in green} \\
\pa{Paul's comments \& questions added in blue} \\
\jr{Jake's comments \& questions added in red}
\end{abstract}
\begin{keyword}
  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
\end{keyword}

@@

(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time. Possible candidates - bluefin tuna vs. halibut comparison to show variation).

@@

\pa{
 Problem description resolved in Meeting 3 - note the list of possible causal mechanisms here (reaching agreement to processor plants) was negotiated with some not being acceptable suggestions:

 Empirics suggest not always as responsive as Reed solution. Explore conditions under which that makes sense. Idea is that regulator’s objective sometimes may not be `raw' NPV, but rather NPV with some penalties on fast changes. Possible reasons pure administrative transaction cost of changing policies (reaching agreement), fishermens' preferences for less variable quotas, processing plants' preferences for less variable quotas especially if tied into contracts for canning and so forth. But we do not know what the functional form is and will be a lot of work to estimate it. Here we explore several plausible candidates that each reflect different ways these costs could work. Would be good to know if differences between functional forms is particularly important.
}

@@

  Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
    \begin{equation} 
      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t}, 
    \end{equation}
where $Z_t$ gives the stochastic shocks.  $Z_t$ may be distributed log-normally \footnote{though this violates the self-sustaining property of~\citet{Reed1979}, such that the optimal constant-escapement level $S$ in the stochastic model is greater than the optimal escapement in the deterministic scenario.}

\pa{

Resolved in Meeting 3: Base case for all analyses $ph-c_0E$ where $h=qEx$ and $c_0>0$.

Resolved in Meeting 3: The economic smoothing formulation: $ph - (c_0 E+c_4 E^2)$ will ONLY appear in SI with some figures for comparison. We do not make a big play out of comparing one with the other
}

\begin{equation} 
\Pi_0(x,h) = p h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \label{profit}
\end{equation}

where $h$ is the harvest level, $x$ the stock size, $h/x$ represents
fishing effort, $p$ the price per unit harvest.  The coefficient $c_1$
introduces a quadratic cost to effort, a typical way to introduce
smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 = c_1 = 0$.

Policy cost function: L1, L2, fixed fee, asymmetric, are introduced
as modifications to the cost function that depend on the action
taken in the previous time-step.  (This makes the previous action part
of the state space).   All cost functions are characterized in terms
of the coupling coefficient $c_2$.  (Because $c_2$ takes different units
and strength of interaction under the different functional forms, it is
necessary to calibrate the choice of this coefficient such that these
penalties can be compared directly, as described in the next section.)

\pa{
Resolved in Meeting 3: We will only do comparisons described last time as $L_1$, $L_2$ and fixed. They have new and more descriptive names now. $c_0>0$ in all comparisons please. We do not present the asymmetric comparison.

Resolved in Meeting 3: penalties to apply to h(t) NOT E(t)
}

@@

 Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.

Choice of model parameters

\pa{
  Suggested from Meeting 3:

 Give them more meaningful names.   we suggested

$L_1$ - Variable cost with extent of policy change, case 1 / linear

$L_2$ - Variable cost with extent of policy change, case 2 / quadratic

fixed -  Fixed cost associated with any policy change

 My own suggestion is that rather than calling ALL of the relevant parameters $c_2$, that you than call them $c_1$, $c_2$, $c_3$ and when seeking to refer to them collectively you call them $c_i$

 That is why the suggested parameter on $E^2$ penalties for the SI was $c_4$  This section needs also to introduce the NPV function including discounting. We also resolved in Meeting 3 that we should use a positive discount rate.
}

@@

\jr{

Resolved in meeting 3.

Let $h_0^*$ be the optimal control path for the base case $\Pi_0$ version of the NPV function, $NPV_0$.

Let $h_i^*$ be the optimal control path for one comparator case $\Pi_i$ version of the NPV function, $NPV_i$, e.g. $\Pi_i$ might now be what we called the L1 penalty.

Then our independent variable in Fig. 4 for example is the fraction: $1 - NPV_i(h_i^*) / NPV_0(h_0^*)$

By solving that and using the approach outlined in Figure 2, we obtain the $c_i$ value that we use for a given comparison.

Given what is shown in Figure 2, we should make the focal range of fraction be 0-30\% of the $NPV_0(h_0^*)$ value to avoid a blow-up on $c_i$ for some penalty function forms

Resolved in Meeting 3: we would do this instead of a dimensionality argument OR trying to calibrate on costs arising only from induced changes to controls.
}

\jr{
The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.  Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.  
To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).  By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.  For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.  As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.  Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.  One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.

@@

}
%% end-Jake

@@

\pa{ 
  Figure 3 stays largely as is.  But we also need to see the corresponding x trajectories in a way that makes for easy comparisons but not cluttered axes
}

@@

\pa{ 
 A version of Figure 4 to go in. But limit the range of the fraction on the horizontal axis more.  We need to see the corresponding variance and autocorrelation for x as well as h. Also suggested we might want a panel showing cross-correlation statistic as well x to h variation although depending on what it shows it could perhaps go to SI.
}

@@

\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
\pa{ Must be nonlinear somewhere when adjustment costs exceed profits? }

@@

\pa{

  \textbf{Option 1.}

@@

  We include a version of the results Carl currently shows in his Fig 5 and 6 for the L1 penalty, but we include it also for the other penalty function forms - e.g. using Carl’s suggestion of a box-whisker plot.

Reminder - The two figures compare the performance of the optimal policy when accounting for the policy adjustment costs (maximizing $\Pi_{L_1}$) with what the optimal policy recommendation one would arrive if ignoring these costs (maximizing $\Pi_0$) WHEN scoring the performance of the two control recommendations against $\Pi_{L_1}$.

Fig. 5 shows the breakdown into how the gross yield (ph) and adjustment cost ($c_2 abs(h_t-h_{t-1})$) separately. The policy ignoring costs of policy adjustment gets higher gross yields by tracking the variations more closely but also incurs (even) higher policy adjustment costs. Fig 6 combines the two bits to show the effect on net present value. Distribution of profits and costs under a policy-cost scenario vs profits and costs under Reed solution, by penalty type. Figure~\ref{fig:profits_costs}.
}

\pa{ Keep Figure 5 or its equivalent for one penalty function formulation and talk through what it means and how to interpret it.

Underneath lay out

$$ NPV_i(h_{it}^*) = \sum \frac{p h^*_{it}-c_0E^*_{it}-c(h^*_{it})}{(1+\delta)^t} $$

ALL MINUS

$$ NPV_i(h_{0t}^*) = \sum \frac{p h^*_{0t}-c_0E^*_{0t}-c(h^*_{0t})}{(1+\delta)^t} $$

}

\pa{

 Use labelling on the equations to label:

$p h^*_{it}-c_0E^*_{it} $  as contribution (1 - red in Figure 5)
and $c(h^*_{it})$ as contribution (3 - green in Figure 5) in the first expression

 and then

$p h^*_{0t}-c_0E^*_{0t}$ as contribution (2 - blue )
$c(h^*_{0t}$ as contribution (4 - mauve) in the second expression

Then cost of assuming penalties when they are not actually there, i.e. induced cost of controls is (2) - (1),  blue - red cost of assuming no penalties when they are present is [1-3] - [2-4]. Finally tabulate separately for each of $\Pi_1$, $\Pi_2$, $\Pi_3$

rows: $\sigma_{\epsilon}$ low, medium, high

columns: $c_i$ values corresponding to fraction NPV or 90\%, 80\%, 70\%

Cells: (2)-(1) AND [1-3]-[2-4] all divided by $NPV_0(h^*_{0t})$ to make them dimensionless

(alternatively just draw three versions of Fig. 5 if not much is going on as we scope parameter space in this way.)

This option would let one answer:

@@

 We populate a table that organizes columns by the ``Actual functional form of adjustment costs'' and the rows into ``Assumed functional form of adjustment costs.'' The types of functional form in both columns and rows would then run ``None, $L_1$, $L_2$ etc.''

 IF we denote the optimal control for objective function $NPV_i$ as being $h^*_i$, then I would populate the Table with the proportions
 $NPV_i(h^*_j) / NPV_i(h^*_i)$
 (i.e. what proportion of the available NPV you still get if assuming the wrong functional form for the adjustment costs).

 The inclusion of the comparison against None means that all of what was being talked about for Option 2 would be captured. In addition it would provide a robustness check on a policy recommendation if uncertain of either the presence of policy adjustment costs or functional form that they should adopt. Specifically, by comparing across rows one could ascertain whether assuming one choice of functional form was likely to lead to large efficiency costs should other assumptions about adjustment costs prove correct. Similarly one could compare across columns to see if one form were particularly problematic in reality.

  I don't know if those are clear – you need to get mired into the document once again a bit to parse it out. I’ll happily discuss with anyone in a bid to shed more light.

 Discussion of these options and alternative suggestions invited.
}

@@

\section{Discussion}
\cdb{Some possible things to discuss: could add others, could remove some.}
\begin{itemize}
\item From Meeting 3: Interest in how the inclusion of these costs would operationally put a population at greater risk of extinction (e.g. if including the transaction costs increases the variance and autocorrelation of N when subject to the optimal policy). Should expect this, because (AH) as the transaction costs become infinite, you would never change your policy which puts you in the world of open loop control; TAC fixed for all time, which we know puts the stock at greater risk of extinction.
\item Alan on the Table looking at the impacts of $\sigma_{\epsilon}$ should flag that might also be good to look at autocorrelated environmental noise and how that affects thing. Here we look at how the optimal policy induces more color in the stock size EVEN though the environmental variability going into it is white noise.
\item (JL) Interpreting  (1), (2), (3), and (4) in terms of how much you would have available to pay the Japanese and Canadians to convince them to participate in an expedited process to change TACs.
\item   Comparison of the optimal policy solution to the Reed model, traditional economic smoothing penalty - which now appears in SI
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and de-stablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
%\item   Impact of symmetric vs asymmetric costs
\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
\end{itemize}
